Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-03 docs/evol.tex
added Panos paper sugestion in the rel work section

>>>>

Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
Specifically, they analyzed the changes of Linux file-system patches to extract
bug patterns and categorize bugs based on their impact. Their findings
indicated that the number of file-system bugs does not die down over time. By
categorizing bugs they also showed the frequency of specific bugs in specific
components.
